Children's Books

### 2024-11-29 paper/paper.qmd
finished observations and coefficients
added citation for lintr and styler

library(tidyverse)
library(palmerpenguins)
library(kableExtra)
library(arrow)
library(readr)
library(rstanarm)
library(modelsummary)
library(dplyr)
library(here)
library(ggplot2)
library(knitr)
library(scales)

@@

Data analysis is performed using Statistical Programming Language R [@citeR] , along with packages `tidyverse` [@citetidyverse], `palmerpenguins` [@citepalmerpenguins], `kableExtra` [@citekableextra], `arrow` [@citearrow], `readr` [@citereadr], `rstanarm` [@citerstanarm], `modelsummary` [@citemodelsummary], `dplyr` [@citedplyr], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `scales` [@citescales].

@@

pp_check(model_file) +
  theme(legend.position = "bottom")
```

>>>>

library(tidyverse)
library(palmerpenguins)
library(kableExtra)
library(arrow)
library(readr)
library(rstanarm)
library(modelsummary)
library(dplyr)
library(here)
library(ggplot2)
library(knitr)
library(scales)
library(testthat)
library(lintr)
library(styler)

@@

Data analysis is performed using Statistical Programming Language R [@citeR] , along with packages `tidyverse` [@citetidyverse], `palmerpenguins` [@citepalmerpenguins], `kableExtra` [@citekableextra], `arrow` [@citearrow], `readr` [@citereadr], `rstanarm` [@citerstanarm], `modelsummary` [@citemodelsummary], `dplyr` [@citedplyr], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `scales` [@citescales] and `testthat` [@testthat]. The code involved in the analysis was styled using `lintr` [@citelintr] and `styler` [@citestyler].

@@

pp_check(model_file) +
  theme(legend.position = "bottom")
